---
title: "Assignment_2"
output:
  word_document: default
  html_document: default
date: "2026-03-19"
---

This is an assignment_2 from week 3 class 2. In this assignment we get to know how to get dummy data, like **airquality** and check its *head* and *tail* to see the shape of the data.

```{r}
airquality
head(airquality)
tail(airquality)
```

## Creating a DataFrame

You can create a *DataFrame*, for example:

```{r}
datas<-data.frame(airquality)
head(airquality)
```

After this conversion we sort the dataframe from *NaN* and *Na* values with `complete.cases`. Then we take **6** sample data from that dataframe. And see the **essential** information about the data.

## Process:

```{r}
good<-complete.cases(airquality)
avldata<-airquality[good,][1:6,]
avldata
str(avldata)
```

## Cleaning the dataframe:
Using `is.na() and !rowSums()` we could clean our dataframe from **NaN and Na**.

## Process:

```{r}
bad <- is.na(datas)
new_data<-datas[!rowSums(bad), ]
new_data
```
## After that we can see the *head* of the dataframe.

```{r}
head(new_data)
```

